\documentclass[11pt]{article}
\usepackage[cm,empty]{fullpage}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{texlogos}
\usepackage{hyperref}

\textheight=10in
% This was started from http://www.constantinos.us/blog/category/latex

\pagestyle{empty}
%\raggedbottom
\raggedright

\urlstyle{same}

% DEFINITIONS FOR RESUME
%\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
%\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{\large #1}} \vspace*{-6pt} \lineunder}

%\newcommand{\lineunder}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
%\newcommand{\lineunder}{\kern2pt\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}


\newcommand{\myline}{\par
  \kern3pt % space above the rules
  \hrule height 0.4pt
  \kern3pt % space between the rules
}

\newcommand{\header}[1]{\textsc{#1} \myline}

\newenvironment{achievements}{\begin{list}{\bf \Large $\cdot$}{\topsep 2pt \itemsep 0pt}}{\vspace*{3pt}\end{list}}
\newenvironment{achievements2}{\begin{list}{\bf \Large $\cdot$}{\topsep 2pt \itemsep 0pt \leftmargin 12pt }}{\vspace*{3pt}\end{list}}
\DeclareRobustCommand{\csharplogo}{\hbox{C\hspace{-0.5ex}
    \protect\raisebox{0.5ex}
    {\protect\scalebox{0.67}{\#}}}}
%END RESUME DEFINITIONS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  \begin{minipage}[b]{3in}
    \textbf{\Huge \sc Nate Dire}  
  \end{minipage}
    & 
  \begin{minipage}[c]{3in}
    P: XXX \\
    E: XXX \\
    W: \url{http://www.linkedin.com/in/ndire}
  \end{minipage} \\
\end{tabular*}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Summary}

\begin{achievements2}
\item Flexible, analytical, and proven data science engineer with strong systems and statistics background.
\item Pre-series A experience at two successful Seattle startups.
\item Ability to independently research, apply, and productize complex algorithms.
\item Experience applying machine learning and NLP end-to-end in a B2B SaaS product.
\item Key contributor to successful high-performance POSIX/ACID clustered file
  system that scaled to 144 nodes and 15~PB.
\item Advanced knowledge of file systems, distributed system, and *nix server programming.
\item Production contributions with AWS, Chef, Clojure, Java, MongoDB, Postgres,
  Python, Ruby, Solr, and Spark.
\end{achievements2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Work History}

\href{http://www.highspot.com}{\bf Highspot}, Seattle, WA \\
{\em Principal Software Engineer} \hfill May 2013 - June 2018
  \begin{achievements}

  \item[] Data Science contributions:
    \begin{achievements2}

    %\item Logistic regression

    \item Evaluated LDA topic model on office documents in both Spark and AWS
      Comprehend.

    \item Implemented matrix factorization recommendations using Spark mllib
      ALS with time-decayed item affinity.  Added vector support in Solr to
      compute preference scores based on user and item vectors.  Plumbed crude
      A/B testing model to evaluate lift.

    \item Built out Relevance KPI Dashboards in AWS QuickSight using custom
      Postgres views.

    \item Provisioned and configured production snapshot environment for
      optimizing MRR via query log replay experiments.

    \item Implemented custom suggested query scheme with fuzzy matching and
      personalization.  Seeded with entity title N-grams.  Used for 20\% of
      queries.

    \item Improved media file relevance with content annotation.  Implemented
      hinted transcription for audio and video using Google Cloud Speech API;
      10-color text search and facets using GraphicsMagick quantization; image
      topic and OCR search using Google Cloud Vision API.

    \item Researched and resolved search pathologies with spell correction,
      multi-term synonyms, exact match boosting, and query sanitization.
      Reduced re-query rate by more than 10\%.

    %\item Facets.  Employed Solr field collapsing to organize office documents
    %based on user's last activity.
 
    \item Worked with Data Scientist to productize slide similarity feature
      based on TF-IDF and cosine similarity of text and images.  Independently
      productized full document similarity with hierarchical agglomerative
      max-link clustering for summarizing engagement analytics by document
      cluster.

    \item Planned multi-language search roadmap.  Added basic tokenization and
      normalization support with testing by native speakers.  Implemented
      language identification by combining CLD library and Google Cloud
      Translation API.

    %\item Worked with Data Scientist to design and implemented Solr custom
    %  function query Java extension to power user feed relevance based on
    %  social context.

    \item Built session analysis pipeline from clickstream logging to DAU
      queries.  Joined client-side and server-side logging.  Decorated links
      for CTR and MRR analysis.

    \item Built business intelligence pipeline from MongoDB to RDS Postgres.
      Currently used for business metrics, billing, and to deliver custom
      analytics to customers.

    \end{achievements2}

  %\item[] Feature contributions:
  %  \begin{achievements2}
  %  \item Facet improvements, bucketing, your activity
  %  \item Audio and Video
  %  \item Global lists
  %  \item Led Content scheduling, archive and restore
  %  \item Reviews and ratings
  %  \item Integrated Diffbot and Thumbnail.ws APIs to provide quality thumbnails on web links.
  %  \end{achievements2}

  \item[] Infrastructure contributions:
    \begin{achievements2}

    \item Eliminated downtime deployments by researching and proposing crude
      rolling deployment scheme.  Established git branching and tagging model
      for releases, along with corresponding application version recorded in
      clickstream log.

    \item Measured and improved email deliverability using Sendgrid and 250ok.
      Implemented open and click tracking via webhook updates.  Prototyped
      recipient tracking via external server.  Designed DKIM/SPF scheme for
      sending with customer email in from header.

    \item Redesigned Solr commit model along with background work queue to be
      more NRT-friendly, reducing average latency by 50\% and eliminating a
      class of outages.  Implemented atomic updates for 100x faster updates to
      numeric fields.

    \item Planned application concurrency roadmap; refactored data layer for
      tombstoning, idempotency, and optimistic updates to MongoDB and Solr,
      including HTTP 409 and 410 responses.

    \item Deployed 8-node Solr cluster behind private ELB using VPC
      ClassicLink.  Deployed attendant Zookeeper cluster to replace single
      instance.  Upgraded Solr approximately yearly from 4.2 to 6.5.  Wrote
      tasks to validate index, balance replicas, and run daily rolling restart.

    \item Expanded MongoDB server to replica set.  Migrated deployment to
      CloudManager.  Set up backup scheme with tasks for developer restores of
      production.  Planned upgrades from 2.4.x to 3.2.x, including Ruby, Java,
      and Clojure library updates.  Proposed and implemented functional
      partitioning scheme with second replica set.

    %\item Researched and evaluated cloud-based monitoring solutions.  Added New
    %  Relic Ruby and Java APM agents to Chef-based AWS deployment.

    %\item Designed and implemented custom hostnames and custom subdomains.

    \end{achievements2}

  \end{achievements}

%{\bf \href{http://www.statfame.com}{StatFame}}, Seattle, WA \\
%  {\em Co-Owner/Developer} \hfill January 2013 - May 2013
%  \begin{achievements}
%  \item Rewrote \csharplogo{} and SQL Server back-end in 1/2 LOC and 5x
%    performance.
%  \item Implemented new import sources and personal URL features from
%    CSS down to SQL; moved web role to Azure and created separate dev stack.
%  \end{achievements}
 
{\bf EMC, \href{http://www.isilon.com}{Isilon Division}} (formerly Isilon Systems), Seattle, WA \\
  {\em Consultant Software Engineer} \hfill April 2011 - March 2013
  \begin{achievements}
  \item Presented clustered file system architecture at EMC World 2011 and 2012.
  \item Wrote 200+ page product internal architecture document in \LaTeX.
  \item Led large cluster scalability roadmap.
  \item Designed and implemented new BSD vnode operation locking to enable
    file system filter API.
  \item Member of product architecture team; met with customers and consulted
    on product deployment configurations.
  \end{achievements}

  {\em Lead Software Engineer} \hfill August 2008 - April 2011
  \begin{achievements}
  \item Independently formed multi-department group to create field product
    configuration tool used by all sales engineers.
  \item Led design and implementation of multithreaded, distributed job engine which runs critical file system jobs on clusters up to 144 nodes.
  \item Led design and implementation of file system SSD strategy.
  \item Planned and executed roadmaps for tiering and integrity features.
  \end{achievements}

  {\em Software Engineer} \hfill March 2003 - August 2008
  \begin{achievements}
  \item Researched and evaluated erasure codes.  Implemented Reed-Solomon
    codes for 4-failure protection, including hand-optimized x86 assembly with
    SSE2 instructions.
  \item Designed and implemented mark-and-sweep collection for orphaned file
    system structures.
  \item Independently researched reliability analysis techniques.  Implemented
    Monte Carlo simulator in \cpluspluslogo{}.
  \item Coordinated Mean-Time-To-Data-Loss (MTTDL) estimation with Marketing, QA, and Operations.
  \end{achievements}

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Education}
\bigskip

\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  \begin{minipage}[t]{0.45\linewidth}
    \href{http://www.whitman.edu}{\bf Whitman College} \\
    B.A. Mathematics, {\em cum laude}, May 1998
    \begin{achievements2}
    \item Phi Beta Kappa
    \item Presented inverse eigenvalue numerical analysis research at 1998 AMS/MAA Annual
      Meeting
    \end{achievements2}

  \end{minipage}
  & 
  \begin{minipage}[t]{0.45\linewidth}
    \href{http://cs.washington.edu}{\bf University of Washington} \\
    M.S. Computer Science, June 2005 \\
    Certificate in Natural Language Technology, March 2016 \\

    {\bf Coursera} \\
    %Machine Learning, March 2014 \\
    Recommenders Specialization, April 2018 \\
  \end{minipage}
  \\
\end{tabular*}

\end{document}

% vim: sw=2:ts=2:
